In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-11 paper/main.tex
Almost all updates

\subsection*{Intracranial influx after intrathecal injection}
To represent molecular influx into the intracranial compartments
following intrathecal injection, without modelling the spinal
compartment explicitly, we prescribe a time-dependent molecular influx
over the interface towards the spinal CSF compartment with the condition
\begin{equation*}
  (D \nabla c - \bm u c ) \cdot \bm{n} = g_{\mathrm{influx}},  \quad \mathrm{on}  \quad \Gamma_{\mathrm{SSAS}}.
\end{equation*}
Here we set
\begin{equation*}
  g_\mathrm{influx}(t) = \frac{m_{\rm tot}}{T_{\rm max}^2 |\Gamma_{\rm SSAS}|} \max(0, T_{\rm max} - |t - T_{\rm max}|), 
\end{equation*}
which expresses a hat-shaped influx function with a peak at $T_{\rm max}$ and a total tracer injection of $m_{\rm tot}$ (\Cref{tab:parameters}).

>>>>

\subsection*{Intracranial influx after intrathecal injection}
To represent molecular influx into the intracranial compartments
following intrathecal injection, without modelling the spinal
compartment explicitly, we prescribe a time-dependent molecular influx
over the interface towards the spinal CSF compartment with the condition
\begin{equation*}
  (D \nabla c - \bm u c ) \cdot \bm{n} = g_{\mathrm{influx}},  \quad \mathrm{on}  \quad \Gamma_{\mathrm{SSAS}}.
\end{equation*}
Here we set
\begin{equation}
  g_\mathrm{influx}(t) = \frac{m_{\rm tot}}{T_{\rm max}^2 |\Gamma_{\rm SSAS}|} \max(0, T_{\rm max} - |t - T_{\rm max}|), 
  \label{eq:g}
\end{equation}
which expresses a hat-shaped influx function with a peak at $T_{\max}$ and a total tracer injection of $m_{\rm tot}$ (\Cref{tab:parameters}). We here consider a fixed $T_{\max} = 1.0$ h in~\eqref{eq:g}, and do not consider the effect of e.g.~reduced pulsatility on spinal transit time.
